A simplified Plackett-Luce likelihood function for rank orders

### 2024-03-22 inst/hankin-ejs.tex
typos

Using $\mathcal{S}=\log(B-1)-B\frac{r+1}{n}$ as an approximate support
thus incurs an error of only $\mathcal{O}(n^{-2})$.  Observing that
$\partial^2\mathcal{S'}/\partial B^2=-(B-1)^{-2}<0$, the evaluate
would be unique; we have
$\hat{B}=\frac{n+r+1}{r+1}+\mathcal{O}\left(n^{-1}\right)$, or
alternatively $\hat{a}=\frac{n}{n+r+1}$.  Compare this with the result
of asking ``what is the probability $p$ that the focal competitor
beats a randomly chosen opponent?'' to which the binomial maximum
likelihood estimate is simply $\frac{n-r}{n}$, agreeing to within
$\mathcal{O}(n^{-2})$.  For repeated observations $r_i,n_i$,
$1\leqslant i\leqslant m$ we would have
\begin{equation}
  \hat{a} = 1-
  \frac{\frac{r_1+1}{n_1}+\cdots+\frac{r_m+1}{n_m}}{m}
  = 1-\overline{\left(\frac{r+1}{n}\right)}.
\end{equation}

@@

\begin{figure}[t]
\includegraphics[width=4in]{plotolymp} % produced by very_simplified_likelihood.Rmd
\caption{Log-likelihood curve for the Bradley-Terry strength of the
  lane-1 runner, olympic qualifying heats 2012-2020 \label{plotolymp}}
\end{figure}

>>>>

Using $\mathcal{S}'=\log(B-1)-B\frac{r+1}{n}$ as an approximate support
thus incurs an error of only $\mathcal{O}(n^{-2})$.  Observing that
$\partial^2\mathcal{S'}/\partial B^2=-(B-1)^{-2}<0$, the evaluate
would be unique; we have
$\hat{B}=\frac{n+r+1}{r+1}+\mathcal{O}\left(n^{-1}\right)$, or
alternatively $\hat{a}=\frac{n}{n+r+1}$.  Compare this with the result
of asking ``what is the probability $p$ that the focal competitor
beats a randomly chosen opponent?'' to which the binomial maximum
likelihood estimate is simply $\frac{n-r}{n}$, agreeing to within
$\mathcal{O}(n^{-2})$.  For repeated observations $r_i,n_i$,
$1\leqslant i\leqslant m$ we would have
\begin{equation}
  \hat{a} = 1-
  \frac{\frac{r_1+1}{n_1}+\cdots+\frac{r_m+1}{n_m}}{m}
  = 1-\overline{\left(\frac{r+1}{n}\right)}.
\end{equation}

@@

\begin{figure}[t]
\includegraphics[width=4in]{plotolymp} % produced by very_simplified_likelihood.Rmd
\caption{Log-likelihood curve for the Bradley-Terry strength of the
  lane-1 runner, Olympic qualifying heats 2012-2020 \label{plotolymp}}
\end{figure}
